\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-11-21 Final Paper/PaperJLin.tex
Asses Africa, Asia, Sothwestern Europe, Middle East, and Central Europe data tables

@@

From the review of literature, we see that there seems to be an ideological divide between people living in rural and urban areas of their respective countries. From case studies, most notably in the United States and Canada, there is a pattern such that the individuals living in rural areas tend to err towards conservatism and residents of urban centers tend to veer towards liberalism. However, given that these are relatively established democracies, I wonder how differences in levels of democratic development, regime age and other ideosyncratic factors that shape a regime influence the divide of political ideologies between urban and rural residents. Therefore, the present research will test three hypotheses relating to the relationship between the place of residence of an individual and their political ideology.

@@

@@

@@

@@

@@

\begin{landscape}
\begin{table}
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Southwestern Europe}}
	\begin{tabulary}{\linewidth}{l c}
		\\
		\hline
		\tb{Place of Residence}& \tb{Bulgaria} \\
		\hline
		Small Town&.5324 \\
		&(.3313) \\
		Suburban& .7821*** \\
		& (.2914) \\
		Urban& .8838** \\
		& (.3590) \\
		Constant& 4.739 *** \\
		& (.2267) \\
		N& 750 \\
		$R^2$&0.0118 \\
		\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table8}
\end{table}
\end{landscape}

\begin{landscape}
\begin{table}
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Pacific Islands}}
	\begin{tabulary}{\linewidth}{l c c c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Australia}&\tb{New Zealand (2011)}&\tb{New Zealand (2014)} &\tb{Philippines}\\
		\hline
		Small Town  & - .2108  & -.2283  &-.1436 &  .6419***  \\      
		& (.1540)   & (.2213) & (.2864)  & (.2060)    \\
		Suburban  & -.1433   & -   & -    & - .1095   \\ 
		& (.1570)   & -  & -    & (.3871)       \\
		Urban  & -.3005** & -.2653  & -.2151 & .3048** \\
		& (.1335) &(.2114)   & (.2406) & (.1526)      \\
		Constant   & 5.372***   & 5.754*** & 5.9674***  & 7.009***   \\
		&(.1219)&(.1826)&(.2207)&(.1030) \\
		N 	 & 3,363   &1,039    & 957   & 1,179  \\
		$R^2$  & 0.0018   &0.0016  &0.0035  &0.0097     \\
		\hline                                       
	\end{tabulary} 
	\\
	\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
	\e{Reference:} A rural place of residence serves as the baseline for comparison
	\label{table10}
\end{table}
\end{landscape}

@@

@@

>>>>

Whereas Figure \ref{figure2} shows a graphical display of the countries represented in this module of the CSES by their level of democracy and regime age, Table \ref{table101} in Appendix \ref{AppendixC} shows this data broken down more specifically, adding the consideration of the regime's electoral formula.

@@

From the review of literature, we see that there seems to be an ideological divide between people living in rural and urban areas of their respective countries. From case studies, most notably in the United States and Canada, there is a pattern such that the individuals living in rural areas tend to err towards conservatism and residents of urban centers tend to veer towards liberalism. However, given that these are relatively established democracies, I wonder how differences in levels of democratic development, regime age and other idiosyncratic factors that shape a regime influence the divide of political ideologies between urban and rural residents. Therefore, the present research will test three hypotheses relating to the relationship between the place of residence of an individual and their political ideology.

@@

\subsubsection{\e{Place Matters} on the Worldwide Scale}

For the first model, a regression was conducted to see if there is a general trend between place and self-placement on a 10-point ideology scale. Furthermore, the regression was conducted separately for each election that was represented in this dataset. Table \ref{table3} shows the results for this regression on the global scale. This general trend suggests that, without considerations of any polity-specific factors, there is a difference between the global rural residents, small town and suburban residents in terms of their political ideologies. The trends described in this table suggests that, on a general level, there lies a difference between where people live and their political attitudes. However, several caveats are present in this analysis. From here, we are assuming that individuals conceptualize the places of residence in a similar fashion across geographic boundaries. Additionally, this analysis does not take into account country-specific measures such as the presence of the different possibilities of residence for the people. As I noted in Tab;e \ref{table2}, not all the countries have respondents from each place of residence as categorized in the CSES. Therefore, it would help to break down the analysis by country.

@@

\subsubsection{\e{Place Matters} By Geographic Region}

When the analysis is broken down by the countries themselves, we see a clearer patterns between place of residence and political attitudes of the respondents to the CSES survey. Each country is displayed and analyzed with their regional neighbors. Additionally, these trends are discussed in context of some key macro variables present for each polity that is displayed in Figure \ref{figure2} and Appendix \ref{AppendixC}.

Table \ref{table4} discusses the patterns seen by place of residence for countries in Central America and Latin America. From the results of the regression, we see that urban residents in Argentina are, on average, more liberal than their rural counterparts. This is slightly the case for Mexico at the time of their 2015 elections, but we do not see these trends elsewhere. When considering the levels of democracy, electoral formula and regime age for these countries, the notable difference between the regimes is the age of the system. Residents of Argentina have been living in a democracy for a longer period of time than the other countries represented in this region.

@@

In Western Europe, as Table \ref{table5} shows, there is a clearer divide between place of residence and political ideologies, such that, for all of the counties displayed in the table, urban residents are significantly more likely to be more left-leaning than their rural counterparts. Additionally, suburban residents in Switzerland and Portugal are also more likely to be more left-leaning than their rural counterparts. Small town residents can be slightly more left-leaning than rural residents in Portugal, Great Britain and Germany. The countries in this region are some of the free-est and oldest democracies in the world. Therefore, individuals here have had a longer time to socialize and develop their opinions based on factors relating to self-interest.

@@

Countries in Northern Europe are also relatively free in terms of their level of democracy and time that such democracy is established. Like their Western European counterparts, Scandinavian countries hold similar governing systems but do not experience similar trends in terms of place of residence and political attitudes. As Table \ref{table6} suggests, Finland is the only country with a sharp urban-rural divide. Iceland's place divide comes with the suburban-rural split between the residents. While there are subtle levels of significance elsewhere, it is clear that there is a regional difference when it comes to how democracy influences individual's political attitudes based on place. In the light of countries of Western Europe, Northern European countries do not see the same patterns fo residence divides even with similar freedoms and levels of democracy. This suggests that there are other differences in these regions that are worth considering.

@@

\begin{landscape}
\begin{table}
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Southwestern Europe}}
	\begin{tabulary}{\linewidth}{l c c c c c c c}
		\\
		\hline
		\tb{Residence}& \tb{Bulgaria}& \tb{Greece ('12)}& \tb{Greece ('15)} & \tb{Montenegro} & \tb{Serbia} & \tb{Romania ('12)} & \tb {Romania ('14)}\\
		\hline
		Small Town&.5324 &-.7220*** &-.1458 & -1.3499*** & .2226 & .1211 & .2699\\
		&(.3313)& (.2656) & (.3484) & (.3282) & (.2098)& (.2304) & (.3097)\\
		Suburban& .7821*** & -1.058*** &-.0685 & -.9444** &.1046 &-.1422 &.1463\\
		& (.2914) &(.2557) & (.3667) & (.4876) &(.2900) & (.5737) & (.4000)\\
		Urban& .8838**& -1.1088*** & -.1737 & -1.4676*** & -.1549 & .7782*** & -.3691\\
		& (.3590)& (.1797) & (.3236) & (.4987) & (.2437) & (.2105) & (.3712)\\
		Constant& 4.739*** &5.5410*** & 4.5961*** &6.7329*** & 5.4643*** & 4.7229*** & 6.4406***\\
		& (.2267) & (.1271)  & (.3089) & (.2409) & (.1239) & (.1438) & (.1890)\\
		N& 750 & 928 & 905 & 450 & 1,094 & 1,192 &714\\
		$R^2$&0.0118 &0.0441& 0.0005 &0.0419 & 0.0020 & 0.130 &0.0037 \\
		\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table8}
\end{table}
\end{landscape}

\begin{table}
\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Eastern Europe}}
	\begin{tabulary}{\linewidth}{l c c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Latvia (2011)} &\tb{Latvia (2014)} \\
		\hline
		Small Town &.1635 &.0560 \\
		&(.2433) & (.2224) \\
		Suburban&- & -.1285 \\
		& - & (.2893) \\
		Urban&-.2292&.0221 \\
		& (.1850) & (.1996) \\
		Constant & 6.2775*** &6.3285*** \\
		& (.1360) & (.1396) \\
		N&787 & 815\\
		$R^2$& 0.0041 &0.0005 \\
		\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table9}
\end{table}

\begin{table}
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Middle East}}
	\begin{tabulary}{\linewidth}{l c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Israel} & \tb{Turkey} \\
		\hline
		Small Town&1.2822*** & .0228 \\
		&(.2427)  & (.3120)\\
		Suburban&1.5019*** &.5457 \\
		& (.2767)  & (.3326 )\\
		Urban &- & .2337\\
		&- & (.2764)\\
		Constant& 4.9193*** &5.7434*** \\
		& (,.2067)  & (.2268)\\
		N&912 & 965\\
		$R^2$&0.0371 & 0.0037 \\
		\hline 
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table10}
\end{table}

\begin{table}
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Africa}}
	\begin{tabulary}{\linewidth}{l c c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Kenya}& \tb{South Africa} \\
		\hline
		Small Town&- &-\\
		&- & -\\
		Suburban&- & -\\
		& - &- \\
		Urban&-1.2690*** &-.06719 \\
		&(.3701)  &(.1664)\\
		Constant&6.7690*** &6.4965*** \\
		& (.1932) & (.1392) \\
		N&506 & 967\\
		$R^2$&0.0228 &0.0002 \\
		\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table11}
\end{table}

\begin{table}
	\centering 
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Asia}}
	\begin{tabulary}{\linewidth}{l c c}
	\\
	\hline
	\tb{Place of Residence} & \tb{Japan} & \tb{South Korea}\\
	\hline
	Small Town &.1898 & -.0347 \\
	&(.1463) & (.2738 )\\
	Suburban&.1717 & -.1176 \\
	& (.1574) & (.4343 )\\
	Urban & .2429* &.3140 \\
	& (.1365) & (.2518)\\
	Constant& 5.4179*** & 5.264*** \\
	& (.1210) & (.2158)\\
	N&1,563 & 717\\
	$R^2$& 0.0020 & 0.0052\\
	\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table12}
\end{table}

\begin{landscape}
\begin{table}
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Pacific Islands}}
	\begin{tabulary}{\linewidth}{l c c c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Australia}&\tb{New Zealand (2011)}&\tb{New Zealand (2014)} &\tb{Philippines}\\
		\hline
		Small Town  & - .2108  & -.2283  &-.1436 &  .6419***  \\      
		& (.1540)   & (.2213) & (.2864)  & (.2060)    \\
		Suburban  & -.1433   & -   & -    & - .1095   \\ 
		& (.1570)   & -  & -    & (.3871)       \\
		Urban  & -.3005** & -.2653  & -.2151 & .3048** \\
		& (.1335) &(.2114)   & (.2406) & (.1526)      \\
		Constant   & 5.372***   & 5.754*** & 5.9674***  & 7.009***   \\
		&(.1219)&(.1826)&(.2207)&(.1030) \\
		N 	 & 3,363   &1,039    & 957   & 1,179  \\
		$R^2$  & 0.0018   &0.0016  &0.0035  &0.0097     \\
		\hline                                       
	\end{tabulary} 
	\\
	\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
	\e{Reference:} A rural place of residence serves as the baseline for comparison
	\label{table13}
\end{table}
\end{landscape}

@@

\subsection{Considerations of Regime Age,, Level of Democracy, and Electoral Formula}

@@

\section{Regimes Broken Down by Macro Variables}
\label{AppendixC}

\begin{table}
	\centering
	\caption{\tb{Regimes by Level of Democracy, Regime Age, and Electoral Formula}}
	\begin{tabulary}{\linewidth}{l c c c}
		\hline
		\tb{Country} & \tb{Level of Democracy} & \tb{Age of Regime} & \tb{Electoral Formula} \\
		\hline
		Argentina&9&32&Proportional \\
		Australia& 10&112&Majoritarian \\
		Austria&9&24&Proportional\\
		Bulgaria&8&24&Proportional\\
		Czech Republic&9&20&Proportional \\
		Finland&10&71& Proportional \\
		France&9&43&Majoritarian \\
		Germany&10&23&Mixed \\
		Great Britain&10&135&Majoritarian \\
		Greece (2015)&10&40&Proportional \\
		Ireland&10&90&Proportional \\
		Israel&10&60&Proportional \\
		Japan&10&61&Mixed\\
		Kenya&9&11&Majoritarian \\
		Latvia (2014)&8&23&Proportional\\
		Mexico (2015)& 8&18&Mixed\\
		Montenegro&9&6&Proportional\\
		Norway&10&68&Proportional\\
		New Zealand (2014)& 10& 137& Mixed\\
		Peru&9&15&Proportional\\
		Philippines&8&26&Majoritarian\\
		Poland&10&20&Proportional\\
		Portugal&10&39&Proportional\\
		Romania (2014) &9&18& Mixed \\
		Serbia& 8&6&Proportional\\
		Slovakia&10&23&Proportional\\
		Slovenia&10&20&Proportional\\
		South Africa&9&20& Proportional \\
		South Korea&8&24&Mixed\\
		Sweden&10&97&Proportional\\ 
		Switzerland&10&163&Proportional\\
		Turkey&3&32&Proportional\\
		United States&10&203&Majoritarian \\
		\hline
	\end{tabulary}
\\
\e{Source:} Polity IV Project and CSES Macro Report
\label{table101}
\end{table}
